---
title: "MA677 HW1"
author: "Chenghao Meng"
date: "2021/2/9"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1 Reproduce the Experiment

As the book mentioned, they have done a few experiments to reach the conclusion that $m_{min}=69$ and $m_{min}=73$. So, we would like to reproduce the experiments by visualizing the distribution of the function: $\alpha(p)=\sum\limits_{m\leq k \leq n}b(n,p,k)$.

```{r}
# Load the package
pacman::p_load(tidyverse)
options(scipen=200)
```

```{r}
set.seed(1)
k <- seq(60,80,by = 3)
p <- seq(0.4,1,by = 1/100)

# Create empty dataframe
df <- data.frame(k = NA, prob = NA, power = NA)[-1,]

# Use for loop to create the dataframe
for (i in k){
  df <- rbind(df,data.frame(k = paste("m=",i,sep=""),
                            prob = p, 
                            power = cumsum(dbinom(x = i,
                                                    size = 100,
                                                    prob = p))
                            
                            )  
              )
  }
```

```{r}
# Plot the graph
ggplot() + 
  geom_line(data = df,aes(x = prob,y = power, color = k)) + 
  geom_rect(aes(xmin = 0.6,xmax = 0.8,ymin = 0.05,ymax = 0.95),alpha = 0.2) + 
  scale_color_brewer(palette = "Paired",direction = -1) +
  labs(col="m",title = "Power Curve: 60<k<80") + 
  xlab("Probability") + ylab("Power")
```

```{r message=FALSE, warning=FALSE}
df %>% 
  group_by(k) %>% 
  summarise(max_power = max(power),
            min_power = min(power))
```

From the results above, we can see that when $69\leq k \leq 75$, the power curves move accross the bottom and the top limits of the grey box, which are the thresholds of the type I and type II error. So, the smallest and the biggest values for $m$ to thwarts the type I and type II errors are within this range.

# Reproduce Figure 3.7

```{r}
m = c(69,73)
df2 = data.frame(k = NA, prob = NA, power = NA)[-1,]
for (i in m){
  df2 <- rbind(df2,data.frame(k = paste("m=",i,sep=""),
                              prob = p, 
                              power = cumsum(dbinom(x = i,
                                                    size = 100,
                                                    prob = p))
                              )  
               )
  }
```


```{r}
ggplot() + 
  geom_line(data = df2,aes(x = prob,y = power, color = k)) + 
  geom_rect(aes(xmin = 0.6,xmax = 0.8,ymin = 0.05,ymax = 0.95),alpha = 0.2) + 
  scale_color_brewer(palette = "Dark2",direction = -1) +
  labs(col="m",title = "Power Curve: m=69 and m=73") + 
  xlab("Probability") + ylab("Power")
```

For the grey box, the bottom line refers to the critical value of type I error, which is 5%, and the top line refers to the critical value of the type II error, which is 95% $(1-5\%)$.

For the lines, the orange line refers to the smallest $m$ that allows the power curve move across the bottom and the top lines of the grey box, which are the thresholds of type I and type II error. The same, the green line refers to the biggest $m$ that allows the power curve move across the bottom and top of the grey box.